Push-Pull Signal-Function Functional Reactive Programming

### 2012-11-30 Docs/IFL2012/introduction.tex
IFL draft update

\todo{TODO: it would be good to give SOME sense for how an FRP
  evaluation proceeds (e.g. a strawman) before getting into the next para.}

>>>>

An FRP program is generally evaluated by supplying a behavior or signal function
to an evaluation function, which supplies input (in the case of a signal
function) and actuates its outputs as they are produced. For instance, if a
video game is implemented in a signal-function FRP system, the evaluation
function is responsible for obtaining keyboard and mouse inputs and supplying
them to the signal function, and actuating the outputs of the signal function
as graphics on the monitor and sound through the speakers.
